When are Fuzzy Extractors Possible?

### 2014-11-24 info-bounds/FuzzyExtPossibility.tex
added references to some info-theoretic two-random variables stuff

\subsection{Sufficiency of $\Hfuzz$ in Related Settings}
\label{sec:related settings}
The security definition of fuzzy extractors and secure sketches can be weakened to protect only against computationally bounded adversaries~\cite{fuller2013computational}.   In this computational setting, fuzzy extractors and secure sketches can be constructed for the family of all distributions $W$ with superlogarithmic $\Hfuzz$ by using virtual grey-box obfuscation for all circuits~\cite{BitanskyCKP14}. The construction places into $p$ the obfuscated program for testing proximity to $w$ and outputting the appropriate value if the test passes.  In addition to relying on strong assumptions for security (namely, the existence of semantically-secure multilinear maps), this construction is not of practical efficiency. Note that if this construction is used for a secure sketch, $W$ will remain unpredictable conditioned on $p$, but will not have pseudoentropy (see  \secref{sec:feas comp sec sketch} for details).

@@

\paragraph{Organization} The reminder of the paper is organized as follows.  In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.  In \secref{sec:known distributions}, we construct a fuzzy extractor for every known distribution with fuzzy min-entropy.  In Sections~\ref{sec:family of dist} and~\ref{sec:imposs fuzz ext} we provide negative results  for families of distributions for secure sketches and fuzzy extractors, respectively.

@@

\subsection{Fuzzy Extractors for Families of Distributions}\label{sec:fuzz extractor}

In this section, we define fuzzy extractors and secure sketches.  Definitions and lemmas are drawn from the work of Dodis et. al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08} with modifications.  First we allow for error, as discussed in \cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}.  Second, in the \emph{family of distributions} setting we consider an arbitrary family $\mathcal{W}$ of distributions instead of families containing all distributions of a given min-entropy.
%\footnote{Our negative results rule out a family that is a subset of all distributions with given min-entropy and thus rules out all distributions of a given entropy.}  
%This is a generalization of the definition of Dodis et al. which require a fuzzy extractor to work for all distributions of a particular entropy.  
We discuss known distribution algorithms in \secref{sec:known distributions def}.  Let $\mathcal{M}$ be a metric space with distance function $\dis$.

\begin{definition}
\label{def:fuzzy extractor}
An $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$. \gen on input $w\in \mathcal{M}$ outputs an extracted string $\key \in\{0,1\}^\kappa$ and a helper string $p\in\{0,1\}^*$. \rep takes $w'\in\mathcal{M}$ and $p\in\{0,1\}^*$ as inputs.   $(\gen, \rep)$ have the following properties:
\begin{enumerate}
\item \emph{Correctness:} if $\dis(w, w')\leq t$ and $(\key, p)\leftarrow \gen(w)$, then $\Pr[\rep( w', p) = \key] \geq 1-\delta$.
\item \emph{Security:} for any distribution $W\in\mathcal{W}$, if $(\Key,P)\leftarrow\gen (W)$, then $\sd((\Key,P),(U_\kappa,P))\leq \epsilon$.
\end{enumerate}
\end{definition}

\noindent
Fuzzy extractors perform two tasks, information-reconciliation and privacy amplification.  The standard construction is \emph{sketch-and-extract:} the uniform key is extracted from $w$~(using a randomness extractor~\cite{nisan1993randomness}) and the error-tolerance is obtained by using a secure sketch~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}.  Secure sketches produce a string $ss$ that minimally decreases the entropy of $w$, while mapping nearby $w'$ to $w$:
\begin{definition}
\label{def:secure sketch}
An $(\mathcal{M},\mathcal{W}, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$.  \sketch on input $w\in\mathcal{M}$ returns a bit string $ss\in\{0,1\}^*$.  \rec takes an element $w'\in\mathcal{M}$ and $ss\in\{0,1\}^*$.  $(\sketch, \rec)$ have the following properties:
\begin{enumerate}
\item \emph{Correctness}: $ \forall w, w'\in\mathcal{M}$ if $\dis(w,w')\leq t$ then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta.$
\item \emph{Security}: for any distribution $W\in\mathcal{W}$, $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
\end{definition}

\noindent In the above definitions, the errors are chosen before $ss$ (resp., $p$) is known: if the error pattern between $w$ and $w'$ depends on the output of $\sketch$ (resp., $\gen$),  there is no correctness guarantee.  
A fuzzy extractor can be produced from a \emph{secure sketch} and an \emph{average case randomness extractor}:

@@

\begin{lemma}
\label{lem:flat hashing} (Proof in \apref{sec:proof of flat hashing})
Let $W$ be a flat distribution with $\Hoo(W)\ge m$.  Then
\consref{cons:universal hash} is a $(\mathcal{M}, W, m - \log |R|, t)$-known distribution secure sketch with error $\delta \le \frac{\beta_{t}-1}{|R|}$. 
\end{lemma}
\begin{corollary}
Let $n = \log |\mathcal{M}|$.  If $|R| \ge |\beta_{t}|* n^{\omega(1)}$ then \consref{cons:universal hash} is correct with overwhelming probability.  That is, setting $\log |R| = \log \beta_{t} + \omega(\log n)$ suffices.
\end{corollary}

@@

\begin{theorem}
\label{thm:layered hashing}
Let $W$ be a distribution over $\mathcal{M}$ where $n =\log \M$.  Let $\delta>0$ be an function of $n$.  Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions where $|R_i| = (\beta_{t,i}-1) /\delta$.  When $\ell = n$ \consref{cons:leveling} is a $(\mathcal{M}, W, \tilde{m}, t)$-secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.

>>>>

\subsection{Related Settings}
\label{sec:related settings}
\paragraph{Other settings with close readings:  $\Hfuzz$ is sufficient}
The security definition of fuzzy extractors and secure sketches can be weakened to protect only against computationally bounded adversaries~\cite{fuller2013computational}.   In this computational setting, fuzzy extractors and secure sketches can be constructed for the family of all distributions $W$ with superlogarithmic $\Hfuzz$ by using virtual grey-box obfuscation for all circuits~\cite{BitanskyCKP14}. The construction places into $p$ the obfuscated program for testing proximity to $w$ and outputting the appropriate value if the test passes.  In addition to relying on strong assumptions for security (namely, the existence of semantically-secure multilinear maps), this construction is not of practical efficiency. Note that if this construction is used for a secure sketch, $W$ will remain unpredictable conditioned on $p$, but will not have pseudoentropy (see  \secref{sec:feas comp sec sketch} for details).

@@

\paragraph{Correlated rather than close readings}
A different model for the problem of key derivation from noisy sources does not explicitly consider the distance between $w$ and $w'$, but rather views $w$ and $w'$ as samples of drawn from a correlated pair of random variables.   This model is considered in multiple works, including~\cite{wyner1975wire,DBLP:journals/tit/CsiszarK78,DBLP:journals/tit/AhlswedeC93,DBLP:journals/tit/Maurer93}; recent characterizations of when key derivation is possible in this model include \cite{DBLP:conf/asiacrypt/RennerW05} and \cite{DBLP:journals/corr/TyagiW14}.

%The definition of $\Hfuzz$ can be extended to this model (by again thinking of the adversary as choosing the value $w'$ that is most likely to lead to a success).

\paragraph{Organization} The remainder of the paper is organized as follows.  In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.  In \secref{sec:known distributions}, we construct a fuzzy extractor for every known distribution with fuzzy min-entropy.  In Sections~\ref{sec:family of dist} and~\ref{sec:imposs fuzz ext} we provide negative results  for families of distributions for secure sketches and fuzzy extractors, respectively.

@@

\subsection{Fuzzy Extractors and Secure Sketches}\label{sec:fuzz extractor}

In this section, we define fuzzy extractors and secure sketches.  Definitions and lemmas are drawn from the work of Dodis et. al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08} with modifications.  First we allow for error, as discussed in \cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}.  Second, in the \emph{family of distributions} setting we consider an arbitrary family $\mathcal{W}$ of distributions instead of families containing all distributions of a given min-entropy.
%\footnote{Our negative results rule out a family that is a subset of all distributions with given min-entropy and thus rules out all distributions of a given entropy.}  
%This is a generalization of the definition of Dodis et al. which require a fuzzy extractor to work for all distributions of a particular entropy.  
%We discuss known distribution algorithms in \secref{sec:known distributions def}.  
Let $\mathcal{M}$ be a metric space with distance function $\dis$.

\begin{definition}
\label{def:fuzzy extractor}
An $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$. \gen on input $w\in \mathcal{M}$ outputs an extracted string $\key \in\{0,1\}^\kappa$ and a helper string $p\in\{0,1\}^*$. \rep takes $w'\in\mathcal{M}$ and $p\in\{0,1\}^*$ as inputs.   $(\gen, \rep)$ have the following properties:
\begin{enumerate}
\item \emph{Correctness:} if $\dis(w, w')\leq t$ and $(\key, p)\leftarrow \gen(w)$, then $\Pr[\rep(w', p) = \key] \geq 1-\delta$ (note that correctness holds for any $w'$ with probability $1-\delta$ over the coins on $\gen$ and $\rep$, but $w'$ cannot be a function of $p$).
\item \emph{Security:} for any distribution $W\in\mathcal{W}$, if $(\Key,P)\leftarrow\gen (W)$, then $\sd((\Key,P),(U_\kappa,P))\leq \epsilon$.
\end{enumerate}
\end{definition}

\noindent
Fuzzy extractors perform two tasks, information-reconciliation and privacy amplification.  The standard construction is \emph{sketch-and-extract:} the uniform key is extracted from $w$~(using a randomness extractor~\cite{nisan1993randomness}) and the error-tolerance is obtained by using a secure sketch~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}.  Secure sketches produce a string $ss$ that minimally decreases the entropy of $w$, while mapping nearby $w'$ to $w$:
\begin{definition}
\label{def:secure sketch}
An $(\mathcal{M},\mathcal{W}, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$.  \sketch on input $w\in\mathcal{M}$ returns a bit string $ss\in\{0,1\}^*$.  \rec takes an element $w'\in\mathcal{M}$ and $ss\in\{0,1\}^*$.  $(\sketch, \rec)$ have the following properties:
\begin{enumerate}
\item \emph{Correctness}: $ \forall w, w'\in\mathcal{M}$ if $\dis(w,w')\leq t$ then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ (note that correctness holds for any $w'$ with probability $1-\delta$ over the coins of $\sketch$ and $\rec$, but $w'$ cannot be a function of $\sketch(w)$).
\item \emph{Security}: for any distribution $W\in\mathcal{W}$, $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
\end{definition}

\noindent
In the above definitions, the errors are chosen before $ss$ (resp., $p$) is known in order for the correctness guarantee to hold: correctness holds for any $w'$ with probability $1-\delta$ over the coins of the algorithms, but $w'$ cannot be a function of the output of  $\sketch(w)$.

\paragraph{The Case of Known Distribution}
If in the above definitions we take $\mathcal{W}$ to be a one-element set containing a single distribution $W$, then the fuzzy extractor/secure sketch is said to be constructed for a \emph{known distribution}.  In this case, we need to require correctness only for $w$ that have nonzero probability\footnote{We can extend correctness to all of $\mathcal{M}$ by defining $\gen$/$\sketch$ to output the point $w$ as part of $p/ss$ on zero-probability inputs, which will ensure that $\rep$/$\rec$ can always be correct; this does not affect security.}.

Note that we have no requirement that the algorithms are compact or efficient, and so the distribution can be fully known to them. Finding a natural model of specifying distributions that allows for efficient~(yet generic) known distribution constructions of sketches and extractors is an interesting problem.

\paragraph{From Secure Sketches to Fuzzy Extractors}
A fuzzy extractor can be produced from a \emph{secure sketch} and an \emph{average case randomness extractor}:

@@

\begin{lemma}
\label{lem:flat hashing} (Proof in \apref{sec:proof of flat hashing})
Let $W$ be a flat distribution with $\Hoo(W)\ge m$.  Then
\consref{cons:universal hash} is a $(\mathcal{M}, \{W\}, m - \log |R|, t)$-known distribution secure sketch with error $\delta \le \frac{\beta_{t}-1}{|R|}$. 
\end{lemma}
\begin{corollary}
Let $n = \log |\mathcal{M}|$.  If $|R| \ge |\beta_{t}|\cdot n^{\omega(1)}$ then \consref{cons:universal hash} is correct with overwhelming probability.  That is, setting $\log |R| = \log \beta_{t} + \omega(\log n)$ suffices.
\end{corollary}

@@

\begin{theorem}
\label{thm:layered hashing}
Let $W$ be a distribution over $\mathcal{M}$ where $n =\log \M$.  Let $\delta>0$ be an function of $n$.  Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions where $|R_i| = (\beta_{t,i}-1) /\delta$.  When $\ell = n$ \consref{cons:leveling} is a $(\mathcal{M}, \{W\}, \tilde{m}, t)$-known distribution secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.
